Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-03-31 r_scripts/parallel_presentation.Rmd
modify

```{r parallel set}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))

@@

## Another important thing:
Check if they are identical!
```{r, echo=FALSE, warning = FALSE, include = FALSE, message = FALSE}
## write matrix of for loop formed
zip_proportion_df <- data.frame(zip_wrf_proportion)

>>>>

```{r parallel set, echo = FALSE}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))

@@

## Another important thing:
Check if they are identical!
```{r, warning = FALSE, message = FALSE, echo = FALSE}
## write matrix of for loop formed
zip_proportion_df <- data.frame(zip_wrf_proportion)
